Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-25 analysis/paper/paper.Rmd
Update figure sizes

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dev = c("postscript"),
  fig.width = 3.31,
  fig.height = 3.31,
  out.width = "100%",
  dpi = 300
)

@@

## Data Collection and Analysis {-}

@@

Because the data were collected on an ordinal scale, but not evenly spaced, the data were converted to the midpoint value of the percent range for severity. Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity. As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the `MCMCglmm` package [@MCMCglmm2010] in the R programming environment [@R2018].

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dev = c("postscript"),
  fig.width = 6.85,
  fig.height = 6.85,
  out.width = "100%",
  dpi = 300
)

@@

### Data Collection {-}

@@

### Statistical Analysis {-}

Because the severity data were collected on an unevenly spaced ordinal scale, they were converted to the midpoint value of the percent range for severity. Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity.

As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the `MCMCglmm` package [@MCMCglmm2010] in the R programming environment [@R2018].

For each measurement, e.g. 2015 tiller incidence, 2016 tiller incidence, a  single  MCMC chain was run for 50,000 steps, with the first 5000 discarded as burn in. The remaining samples were thinned by taking every one-hundredth sample, yielding 5000 independent draws from the posterior distribution of the  parameters of the model. Convergence of the chains was assessed using the coda package in R. The priors of the variances and covariances of the random effects in the  model are locally non-informative priors [74].
